Estimating individual subjective values of emotion regulation strategies

### 2022-06-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "5630"
bibliography      : ER_ED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
---

@@

``` {r child = "TheoreticalBackground.Rmd"}
```

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

@@

\newpage
\setcounter{figure}{0}

# Figures and figure captions

\newpage
```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```
*Figure 1.* 
Exemplary visualization of two response patterns. 
In the top half, the person has a clear preference for one of the three strategies. 
In the lower half, they have no clear preference and therefore show an inconsistent response pattern. 
This pattern can also be represented by our paradigm.

```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
```
*Figure 2.* 
Block design of the paradigm. 
Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. 
Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place.
All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. 
Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.

@@

*Emotion Regulation Questionnaire.* 
Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].

@@

*Brief Self-Control Scale.* 
As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used. 
It comprises 13 items (e.g., “I am good at resisting temptations”) with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me). 
The scale shows acceptable internal consistency (Cronbach’s $\alpha=.81$)[@Sproesser2011] .

@@

\newpage
## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
ANOVA:

@@

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```
## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```
## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrViewPilot)
```
```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevViewPilot)
```
## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrRegPilot)
```
```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevRegPilot)
```
## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

>>>>

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "6233"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

```{=tex}
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
```

------------------------------------------------------------------------

@@

```{r child = "TheoreticalBackground.Rmd"}
```

@@

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
\newpage

@@

```{=tex}
\newpage
\setcounter{figure}{0}
```
# Figures and figure captions

```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```

*Figure 1.* Exemplary visualization of two response patterns.
In the top half, the person has a clear preference for one of the three strategies.
In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
This pattern can also be represented by our paradigm.

```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
```

*Figure 2.* Block design of the paradigm.
Every participant starts with two "active viewing" blocks containing neutral (Block 1) and negative (Block 2) pictures.
Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
After, the discounting procedure takes place.
All three regulation strategies are pairwise compared.
Before the last block, participants can decide which regulation strategy they want to reapply.
Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.

@@

*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].

@@

*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .

@@

## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"

ANOVA:

@@

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```

## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrViewPilot)
```

```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevViewPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrRegPilot)
```

```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevRegPilot)
```

## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}
